
\documentclass[12pt]{article}
\usepackage{amsmath, amssymb, geometry}
\geometry{margin=1in}

\title{Coherological Extension of the Schrödinger Equation: A Symbolic Framework for Quantum Drift}
\author{Hew Carroll \\}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
We introduce a symbolic extension to the Schrödinger equation based on the principles of coherology, a proposed framework for understanding structural coherence across drift and transformation. By defining a coherence functional \( C(t) \), which reflects the stability or dispersion of the wavefunction in space, we modify the standard quantum evolution to include a recursive inhibition term. This addition represents symbolic resistance to collapse and decoherence, offering a pathway to integrate symbolic alignment into quantum foundations.
\end{abstract}

\section{Introduction}
Standard quantum mechanics models the evolution of isolated systems using the time-dependent Schrödinger equation. However, the mechanisms behind wavefunction collapse, decoherence, and observer effect remain conceptually unresolved. Coherology, a symbolic framework concerned with the preservation of coherence across transformation, offers tools to address these gaps without violating physical law.

\section{Modified Schrödinger Equation}
We begin with the time-dependent Schrödinger equation:
\begin{equation}
i\hbar \frac{d\psi(t)}{dt} = H(\psi(t))
\end{equation}

We propose a coherological extension:
\begin{equation}
i\hbar \frac{d\psi(t)}{dt} = H(\psi(t)) - i\hbar \frac{dC(t)}{dt}
\end{equation}
where \( C(t) \) is a coherence functional representing the symbolic drift and structural integrity of the wavefunction.

\section{Definition of the Coherence Functional}
We define the coherence functional as:
\begin{equation}
C(t) = \int_{-\infty}^{\infty} \left| \frac{\partial \psi(x,t)}{\partial x} \right|^2 dx
\end{equation}
This captures the spatial dispersion of the wavefunction. As dispersion increases, coherence decays, and the system becomes more susceptible to collapse or transition.

\section{Interpretation}
The term \( -i\hbar \frac{dC(t)}{dt} \) acts as an ethical inhibitor of symbolic drift. If coherence is stable, quantum evolution proceeds classically. If coherence destabilizes, the term contributes to symbolic collapse without requiring external measurement.

\section{Applications and Implications}
This model offers new ways to interpret decoherence, entanglement, and quantum measurement. It also provides a framework for integrating symbolic AI, ethical alignment, and recursive inhibition into quantum computational systems.

\section{Conclusion}
The coherological extension provides a bridge between symbolic systems and quantum theory, not by replacing existing physics, but by offering a deeper structural understanding of coherence, drift, and collapse. Future work will refine \( C(t) \) for discrete systems and explore connections to entropy, thermodynamics, and emergence.

\end{document}
